MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
add analysis data software project section, fix acknowledgements -- paper
add ideas for data analysis as code -- paper
help needed! see https://github.com/ohnosequences/metagenomica/issues/26#issuecomment-140128079

@@

The two first authors are funded by INTERCROSSING (Grant 289974).

>>>>

\subsection{Data analysis as a software
project}\label{data-analysis-as-a-software-project}

\textbf{IDEAS}

\begin{itemize}
\tightlist
\item
  the user needs to write code, a repo would be nice, AWS account
\item
  there's some sort of conf required for the AWS account (add users,
  roles, permissions, whatever)
\item
  Why this is a good thing (or should this just be in Discussion)
\item
  something else?
\end{itemize}

@@

\emph{Funding:} The two first authors are funded by INTERCROSSING (Grant
289974).
